The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-23 Writeup/paper_v3.tex
figure* -> figure

\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}

\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

@@

\rachel{Overall comment: the figures need a {\em lot} of work.  First,
  they should be in the same order as they are referenced in the
  text.  Second, they need to be sensibly referenced in the text; you
  can't say ``as we see\dots'' without having a clear statement that
  we should be looking at Fig.~4 (or whatever).  In all
  cases, the font size is way too small, so you should enlarge it.
  The rule of thumb for MNRAS and other journals is that the font size
  in the figures should appear the same size as the font in the text
  of the paper.  (This is true for axis labels, tick labels, and text
  in the legend.)  You also need to write good captions, because some
  people will not really read the paper, just the captions.  MNRAS
  does not use the subfigure environment, so you should remove it.
  Just have the figures on top of or next to each other, and then in
  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.}
\arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
\rachel{No, just move the figures a bit earlier in the text.  It's okay for them to show up slightly before you actually discuss them.  The references really should be last.}
\section{Introduction}
\label{S:intro}

@@

\subsection{Finding overdensities}
\label{sub:overdensities}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.0$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-squared distribution given by
\begin{equation}
 p_1(z) \sim z^{a-1}\exp({-bz})
\end{equation}
and the function given by
\begin{equation}
 p_2(z) \sim z^2\exp{\left(-\left(\frac{z}{z_0}\right)^{1.5}\right)}
\end{equation}
that was first presented by~\cite{Redshift_modelling} as fits to the
redshift histograms. The normalization constants depend not only on the parameters but also on the lower and the upper limit of the redshifts considered. \rachel{(To avoid ambiguity, you should use avoid
  using the same symbol in both equations.  For example you could turn
  the $b$'s into $b_1$ and $b_2$.  Also, the normalization factors out
  front do not matter - they are not something that you fit for.  I
  would say $p(z)\propto$\dots to avoid 
  the need for a normalization for which you are not actually fitting.)} Here $a,b$ and $z_0$ are free parameters that are to be determined.
%\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$. Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift. 
We choose our bins to be $0.05$ wide starting from $z=0.3$. 
%\rachel{Were you going to use other fitting functions as a test of the method?  If so, you should introduce them here.}

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited ($m_\text{F814W}\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

\subsection{Volume limiting}
\label{sub:volumelimiting}
COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on $K$-corrected $F814W$-band magnitudes, denoted as $M_\text{F814W}$.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
  self-consistent throughout the text.}\arun{I think they call it
  $I_{814}$, so $I$.}
\rachel{But you are still being ambiguous in sometimes calling it $I$
  and other times F814W.  Pick one.}
Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2-D histogram of galaxies in apparent magnitude ($m$) and absolute magnitude ($M_\text{F814W}$) space.}
   \label{fig:2Dhist}
 \end{figure}

@@

\begin{figure*}
 \centering
 \includegraphics[width=2.4\columnwidth]{figure_generated}
 \caption{Stellar-mass distribution for various flux-limited samples in three redshift ranges are plotted. Bins have been chosen so as to make the comparison easier with 
          a study of SMF in the same FOV \citep{Tomczak_SMF}. At high mass, the distributions are the same for various flux limits indicating that the samples are complete in that mass range. The curves begin to separate at low masses on account of incompleteness, which determines where the mass cutoff should be to volume-limit the sample.}
 \label{fig:smf}
\end{figure*}

@@

We first compare the distribution of the axis ratio in \emph{all}
overdense bins and \emph{all} underdense bins in
Fig.~\ref{fig:axisratio_all}. \rachel{How was the volume-limiting
  carried out for this?  You should say the answer to this question
  for all figures.} Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of~\cite{Claire_Fits}.
The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
The p-value from both the KS and AD tests are well below 0.05
(\rachel{give the actual numbers!} \arun{It's in the table.}
\rachel{The text does not seem to mention the table at all.  If the
  readers are to get the numbers from it, then you need to refer to it
here and any other place where it is relevant.}), 
so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.

@@

\begin{figure*}
 \centering
 \includegraphics[width=2.3\columnwidth]{axis_ratio_all_all}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
 \caption{The distributions of axis ratios of galaxies in \emph{all} overdense (OD) and \emph{all} underdense (UD) regions in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right). The upper panels show the histogram
 and the botom panels show the empirical cumulative distribution function (ECDF). $p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table. \ref{table:pvalues_all}. The difference between the CDFs turn out to be statistically significant.}
 \label{fig:axisratio_all}
\end{figure*}

@@

\begin{figure*}
 \centering
 a) \includegraphics[width=0.9\columnwidth]{rms_ellip1.eps} \
 b) \includegraphics[width=0.9\columnwidth]{rms_ellip2_noevolution.eps} \\
 \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
          are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:rms_ellip}
\end{figure*}

\begin{figure*}
 \centering
 a) \includegraphics[width=0.9\columnwidth]{rms_ellip1_Bbandevolution_masscut.eps} \
 b) \includegraphics[width=0.9\columnwidth]{rms_ellip2_Bbandevolution_masscut.eps} \\
 \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the sample where the luminosity cut evolves by -1.23 per unit redshift (\s$2$) and the unfilled
          points correspond to the sample obtained from stellar mass cuts (\s$3$).}
 \label{fig:rms_ellip_Bband_mass}
\end{figure*}

@@

When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed. We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}. 
Such a trend is not observed in axis ratios based on second moments. 
For other morphological parameters, we do not the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}. We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure*}
 \centering
 \includegraphics[width=\columnwidth]{median_sersicn}
 \includegraphics[width=\columnwidth]{median_sersicn(2)}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure*}

\begin{figure*}
 \centering
 \includegraphics[width=\columnwidth]{median_dvcbtt}
 \includegraphics[width=\columnwidth]{median_dvcbtt(2)}
  \caption{Median values of the \btt ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_dvcbtt}
\end{figure*}

>>>>

%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
\newcommand{\rachel}[1]{}
%\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
\newcommand{\arun}[1]{}
\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

@@

% \rachel{Overall comment: the figures need a {\em lot} of work.  First,  they should be in the same order as they are referenced in the  text.  Second, they need to be sensibly referenced in the text; you  can't say ``as we see\dots'' without having a clear statement that  we should be looking at Fig.~4 (or whatever).  In all  cases, the font size is way too small, so you should enlarge it.  The rule of thumb for MNRAS and other journals is that the font size  in the figures should appear the same size as the font in the text  of the paper.  (This is true for axis labels, tick labels, and text  in the legend.)  You also need to write good captions, because some  people will not really read the paper, just the captions.  MNRAS
%         does not use the subfigure environment, so you should remove it.  Just have the figures on top of or next to each other, and then in  the caption refer to ``Top panel'' and ``Bottom panel'' or whatever.} 
%         \arun{Results have too many figures and they overlap with the bibliography. I think we should put some of the figures explicitly after the references?}
% \rachel{No, just move the figures a bit earlier in the text.  It's okay for them to show up slightly before you actually discuss them.  The references really should be last.}
\section{Introduction}
\label{S:intro}

@@

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited ($m_\text{F814W}\le 23.5$) sample with bins that are 0.05 wide. Two analytical functions with best fit parameters are plotted over it.\
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) = N/N_{\text{mod}}$ with each functional form as the model for each redshift bin.}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.0$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-squared distribution given by
\begin{equation}
 p_1(z) \sim z^{a-1}\exp({-bz})
\end{equation}
and the function given by
\begin{equation}
 p_2(z) \sim z^2\exp{\left(-\left(\frac{z}{z_0}\right)^{1.5}\right)}
\end{equation}
that was first presented by~\cite{Redshift_modelling} as fits to the
redshift histograms. The normalization constants depend not only on the parameters but also on the lower and the upper limit of the redshifts considered. 
\rachel{(To avoid ambiguity, you should use avoid   using the same symbol in both equations.  For example you could turn   the $b$'s into $b_1$ and $b_2$.  Also, the normalization factors out  front do not matter - they are not something that you fit for.  I would say $p(z)\propto$\dots to avoid   the need for a normalization for which you are not actually fitting.)} 
\arun{Done.}
Here $a,b$ and $z_0$ are free parameters that are to be determined.
%\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$. Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift. 
We choose our bins to be $0.05$ wide starting from $z=0.3$. 
%\rachel{Were you going to use other fitting functions as a test of the method?  If so, you should introduce them here.}

@@

@@

\subsection{Volume limiting}
\label{sub:volumelimiting}
\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2-D histogram of galaxies in apparent magnitude ($m_\text{F814W}$) and absolute magnitude ($M_\text{F814W}$) space.}
   \label{fig:2Dhist}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of $M_\text{F814W}$ for various flux-limited samples are plotted together. The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
   \label{fig:2Dhist}
 \end{figure}

COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on $K$-corrected $F814W$-band magnitudes, denoted as $M_\text{F814W}$.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
  self-consistent throughout the text.}\arun{I think they call it
  $I_{814}$, so $I$.}
\rachel{But you are still being ambiguous in sometimes calling it $I$
  and other times F814W.  Pick one.}
Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}

@@

@@

\begin{figure*}
 \centering
 \includegraphics[width=2.4\columnwidth]{SMF}
 \caption{Stellar-mass distribution for various flux-limited samples in three redshift ranges are plotted. Bins have been chosen so as to make the comparison easier with 
          a study of SMF in the same FOV \citep{Tomczak_SMF}. At high mass, the distributions are the same for various flux limits indicating that the samples are complete in that mass range. The curves begin to separate at low masses on account of incompleteness, which determines where the mass cutoff should be to volume-limit the sample.}
 \label{fig:smf}
\end{figure*}

@@

\subsection{Axis-ratios} 
\begin{figure*}
 \centering
 \includegraphics[width=2.3\columnwidth]{axis_ratio_all}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_Bbandevolution.eps}
 %\includegraphics[width=0.66\columnwidth]{axis_ratio_all_masscut.eps}
 \caption{The distributions of axis ratios of galaxies in \emph{all} overdense (OD) and \emph{all} underdense (UD) regions in the case of luminosity-selected sample (left), luminosity-selected with B-band evolution taken into account (center) and stellar-mass-selected sample (right). The upper panels show the histogram
 and the botom panels show the empirical cumulative distribution function (ECDF). $p$-values are computed using these CDFs using the Kolmogorov-Smirnov and Anderson-Darling tests and are given in Table. \ref{table:pvalues_all}. The difference between the CDFs turn out to be statistically significant.}
 \label{fig:axisratio_all}
\end{figure*}

@@

@@

We first compare the distribution of the axis ratio in \emph{all}
overdense bins and \emph{all} underdense bins in Fig.~\ref{fig:axisratio_all}.
\rachel{How was the volume-limiting carried out for this?  You should say the answer to this question  for all figures.} 
\arun{The caption mentions it.}
Unless otherwise mentioned, the axis ratios refer to the values obtained using the method of~\cite{Claire_Fits}.
The cumulative distinction functions are also plotted alongside in order to be able to visualize the `distance' between the distributions.
Referring to the first two rows in Table~\ref{table:pvalues_all}, we see that the p-values from both the KS and AD tests are well below 0.05
(\rachel{give the actual numbers!} 
\arun{It's in the table.} 
\rachel{The text does not seem to mention the table at all.  If thereaders are to get the numbers from it, then you need to refer to it here and any other place where it is relevant.}), 
\arun{Done.}
so we reject the `null hypothesis' that the overdense and underdense regions have same axis ratio distributions at 95\% significance level.

\begin{figure}
 %\centering
 a) \includegraphics[width=1.1\columnwidth]{rms_ellip1.eps} \
 b) \includegraphics[width=1.1\columnwidth]{rms_ellip2_noevolution.eps} \\
 \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
          are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:rms_ellip}
\end{figure}

\begin{figure}
 %\centering
 a) \includegraphics[width=1.1\columnwidth]{rms_ellip1_Bbandevolution_masscut.eps} \
 b) \includegraphics[width=1.1\columnwidth]{rms_ellip2_Bbandevolution_masscut.eps} \\
 \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the sample where the luminosity cut evolves by -1.23 per unit redshift (\s$2$) and the unfilled
          points correspond to the sample obtained from stellar mass cuts (\s$3$).}
 \label{fig:rms_ellip_Bband_mass}
\end{figure}

@@

When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed. We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}. 
Such a trend is not observed in axis ratios based on second moments. 
For other morphological parameters, we do not the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}. We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure}
 %\centering
 \includegraphics[width=1.1\columnwidth]{median_sersicn}
 \includegraphics[width=1.1\columnwidth]{median_sersicn(2)}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure}

\begin{figure}
 %\centering
 \includegraphics[width=1.1\columnwidth]{median_dvcbtt}
 \includegraphics[width=1.1\columnwidth]{median_dvcbtt(2)}
  \caption{Median values of the \btt ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_dvcbtt}
\end{figure}
